### 2013-06-12 menger.tex
Proved Galvin's result, for Cov_CS

  \begin{definition}
    In the two-player game $\rothgame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $O$ choosing an open set $U_n\in\mathcal{U}_n$. $O$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
  \end{definition}

@@

    To show $(b)\Rightarrow(c)$, if $X$ is scattered, suppose during a particular round $n$, player $O$ observes that the uncovered subspace $Y \subseteq X$ is nonempty. Then as $Y$ is also compact scattered,  select one of the finite points in $Y^{\rank(Y)-1}$, label it $x_n$, and choose an open set containing $x_n$ from the given cover.

    We claim that if $O$ follows this strategy, player $O$ will observe that the uncovered subspace $Y\subseteq X$ is empty during some round. If not, consider the $x_n$ chosen by $Y$ by the end of the game - the rank of each point within $X$ is nonincreasing, and does not contain a constant final sequence, contradiction.

@@

  \begin{theorem}
    The following are equivalent for points-$G_\delta$ $X$:
      \begin{enumerate}[(a)]
        \item $O\win\rothgame{X}$
        \item $O\markwin\rothgame{X}$
        \item $|X|=\omega$
      \end{enumerate}
  \end{theorem}

  \begin{proof}
    $(c)\Rightarrow(b)\Rightarrow(a)$ are all trivial. Galvin has shown $(a)\Rightarrow(c)$ in \textit{Indeterminacy}, but a direct proof follows.

    Suppose $X$ is uncountable: define open sets $G_{x,m}$ for $x\in X$ and $m<\omega$ such that $\{x\}=\bigcap_{m<\omega} G_{x,m}$. Let $\mc{U}_m = \{G_{x,m} : x\in X \}$.
      \[
        A = \{ x \in X : \exists \<m_0,\dots,m_{n-1}\>\in\omega^{<\omega} ( 
          \sigma(\mc{U}_{m_0},\dots,\mc{U}_{m_{n-1}})=G_{x,m_{n-1}} )\}
      \]
    Since $|A|=\omega$, choose $x\in X\setminus A$, and during round $n$, playasdf. TODO finish
  \end{proof}

>>>>

  \begin{definition}
    In the two-player game $\rothgame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $S$ choosing an open set $U_n\in\mathcal{U}_n$. $S$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
  \end{definition}

@@

    To show $(b)\Rightarrow(c)$, if $X$ is scattered, suppose during a particular round $n$, player $S$ observes that the uncovered subspace $Y \subseteq X$ is nonempty. Then as $Y$ is also compact scattered,  select one of the finite points in $Y^{\rank(Y)-1}$, label it $x_n$, and choose an open set containing $x_n$ from the given cover.

    We claim that if $S$ follows this strategy, player $S$ will observe that the uncovered subspace $Y\subseteq X$ is empty during some round. If not, consider the $x_n$ chosen by $Y$ by the end of the game - the rank of each point within $X$ is nonincreasing, and does not contain a constant final sequence, contradiction.

@@

  \begin{definition}
    In the two-player game $\altrothgame{X}$ player $P$ chooses points $x_n\in X$, followed by player $O$ choosing an open neighborhood $U_n$ of $x_n$. $P$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
  \end{definition}

  \begin{theorem} $\altrothgame{X}$ is equivalent to $\rothgame{X}$. That is:

    \begin{itemize}
      \item $P\win\altrothgame{X}$ if and only if $S\win\rothgame{X}$
      \item $O\win\altrothgame{X}$ if and only if $C\win\rothgame{X}$.
    \end{itemize}
  \end{theorem}

  \begin{proof}
    Due to Galvin.

    \begin{itemize}
      \item
      Let $\sigma$ be a strategy for $S$ in $\rothgame{X}$.

      We define a strategy for $P$ in $\altrothgame{X}$ as follows: during round $0$, $P$ chooses a point $x_0$ for which every open neighborhood is of the form $U_0 = \sigma(\mc{U}_0)$ for some open cover $\mc{U}_0$. (If not, let $U_x$ witness for every $x\in X$, and note that $\sigma(\{U_x:x\in X\})$ is a contradiction.)

      During round $n+1$, $P$ chooses point $x_{n+1}$ for which every open neighborhood is of the form $U_{n+1}=\sigma(\mc{U}_0,\dots,\mc{U}_n,\mc{U}_{n+1})$ for some open cover $\mc{U}_{n+1}$. (If not, let $U_x$ witness for every $x\in X$, and note that $\sigma(\mc{U}_0,\dots,\mc{U}_n,\{U_x:x\in X\})$ is a contradiction.)

      If $\sigma$ was a winning strategy for $S$, then the open sets chosen by $P$ are of the form $\{\sigma(\mc U_0),\sigma(\mc U_0,\mc U_1),\dots\}$ and are an open cover of $X$.

      \item
      Let $\sigma$ be a strategy for $P$ in $\altrothgame{X}$.

      We define a strategy for $S$ in $\rothgame{X}$ as follows: during round $n$, if $S$ has chosen $U_0,\dots,U_{n-1}$ in previous rounds, $S$ chooses an open set covering the point $\sigma(U_0,\dots,U_{n-1})$. If $\sigma$ was a winning strategy for $P$, then for any open sets $U_0,U_1,\dots$ containing $\sigma(\cdot),\sigma(U_0),\dots$, the collection $\{U_0,U_1,\dots\}$ is a cover for $X$.

      \item
      Let $\sigma$ be a strategy for $C$ in $\rothgame{X}$.

      We define a strategy for $O$ in $\altrothgame{X}$ as follows: during round $n$, if $O$ has chosen $U_0,\dots,U_{n-1}$ in previous rounds, $O$ chooses an open set from the cover $\sigma(U_0,\dots,U_{n-1})$ containing the point chosen by $P$ that round. If $\sigma$ was a winning strategy for $C$, then for any open sets $U_0,U_1,\dots$ from the covers $\sigma(\cdot),\sigma(U_0),\dots$, the collection $\{U_0,U_1,\dots\}$ is not a cover for $X$.

      \item
      Let $\sigma$ be a strategy for $O$ in $\altrothgame{X}$.

      We define a strategy for $C$ in $\rothgame{X}$ as follows: during round $0$, $C$ chooses $\mc{U}_0 = \{\sigma(x) : x\in X\}$. In response, $S$ chooses some $\sigma(x_0)$. During round $n+1$, if $S$ has chosen $\sigma(x_0),\dots,\sigma(x_0,\dots,x_n)$ in previous rounds, $C$ chooses $\mc{U}_{n+1} = \{\sigma(x_0,\dots,x_n,x) : x\in X\}$. If $\sigma$ was a winning strategy for $O$, then $\{\sigma(x_0),\sigma(x_0,x_1),\dots\}$ is not a cover for $X$.

    \end{itemize}
  \end{proof}

  \begin{theorem}
    The following are equivalent for points-$G_\delta$ $X$:
      \begin{enumerate}[(a)]
        \item $S\win\rothgame{X}$
        \item $S\markwin\rothgame{X}$
        \item $|X|=\omega$
      \end{enumerate}
  \end{theorem}

  \begin{proof}
    $(c)\Rightarrow(b)\Rightarrow(a)$ are all trivial. Galvin has shown $(a)\Rightarrow(c)$ in \textit{Indeterminacy}, but a direct proof follows. Let $\sigma$ be a strategy for $S$ in $\rothgame{X}$.

    Let $G_{x,m}$ designate open sets such that $\{x\}=\bigcap_{m<\omega}G_{x,m}$ for all $x\in X$.

    Suppose for $s\in\omega^{<\omega}$, $\mc U_t$ is defined for each $t\leq s$. Then $C$ may find a point $x_s$ such that for each $m<\omega$, there exists an open cover $\mc U_{s\concat\<m\>}$ where $\sigma(\mc U_{s\rest1},\dots,\mc U_{s},\mc U_{s\concat\<m\>})=G_{x_s,m}$. (If not, let $m(x)$ witness the contrary for each $x$, and consider $\sigma(\mc U_{s\rest0},\dots,\mc U_s,\{G_{x,m(x)}:x\in X\})$ to see the contradiction.)

    If $x\not\in\{x_s:s\in\omega^{<\omega}\}$, then $C$ may counter the strategy $\sigma$ by choosing $f\in\omega^\omega$ where $x\not\in G_{x_{f\rest n},f(n)}$, and playing $\mc U_{f\rest1},\mc U_{f\rest2},\dots$, for which 
      \[
        x\not\in 
        \bigcup_{n<\omega} G_{x_{f\rest n},f(n)}=
        \bigcup_{n<\omega} \sigma(\mc U_{f\rest1},\dots,\mc U_{f\rest n+1})
      \]

    Thus if $\sigma$ is a winning strategy, then $X=\{x_s:s\in\omega^{<\omega}\}$ is countable.
  \end{proof}
